Satellite Alignments in the Local Group

### 2017-07-11 paper/paper.tex
references
alignments

We also find the place IS and LGS pairs into the cosmic web as quantified by the deformation tensor
\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
This method computes a cartesian grid the tensor 
\begin{equation}
T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j},
\end{equation}
%
where $\phi$ is a pseudo-gravitational potential that follows the
Poisson equation $\nabla^2\phi=\delta$, with $\delta$ the DM matter
overdentisy, and the $r_i$ coordinates correspond to a cartesian
system with $i=1,2,3$.

@@

\begin{equation}
{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the
positions pof the host DM halo, $\bf{1}$ is the unit matrix,  and
${\bf r}^T$ is the transposed vector $\bf{r}$. 
We finally compute the eigenvalues and eigenvector of this tensor.

@@

We fit satellite planes around each galaxy in the pair by randomly
generating 10000 unit vectors over the  sphere, each vector
representing the direction perpendicular to a plane passing through
the main galaxy's center of mass. 
We compute the dot product of the unit vector with the position vector
for each satellite, this scalar gives us the satellite distance to the
plane. 
The best plane is determined by the vector that gives the lowest
position satellite distance dispersion. 
We take the dispersion value as a measure of the plane's width.
For comparison we also store the value and direction giving the
highest distance dispersion.

@@

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$M_{\star}$ & $10^{10}$\Msun & Stellar mass\\
$N_s$ & & Number of satellites with $M_V<-9$\\
$a > b> c$ & & Inertia tensor eigenvalues. \\
$\hat{s}_1$, $\hat{s}_2$, $\hat{s}_3$ & & Inertia tensor eigenvectors. \\
$\beta$  &  & Satellite Velocity Anisotropy\\
$\sigma_s$ & kpc & Plane width\\
$\lambda_1>\lambda_2>\lambda_3$ &  & Hessian Matrix
eigenvalues\\
$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ & - & Hessian Matrix
eigenvectors\\ 
$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\

\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}

@@

>>>>

We place the LGA pairs into the cosmic web as quantified by the
deformation tensor  
\citep{2007MNRAS.375..489H,2009MNRAS.396.1815F}.
This method computes a cartesian grid the tensor 
\begin{equation}
T_{ij} \equiv \frac{\partial^2\phi}{\partial r_i \partial r_j},
\end{equation}
%
where $\phi$ is a pseudo-gravitational potential that satisfies the
Poisson equation $\nabla^2\phi=\delta$, with $\delta$ the DM matter
overdentisy, and the $r_i$ coordinates correspond to a cartesian
system with $i=1,2,3$.

@@

\begin{equation}
{\bf{\bar{I}}} = \sum_{k \in V}[(\bf{r}_i - \bf{r}_0)^2\cdot \bf{1} -
  (\bf{r}_i-\bf{r}_0)\cdot (\bf{r}_i - \bf{r}_0)^{T}],
\end{equation}
%
where $k$ indexes the set of satellites of interest
$\bf{r}_k$ are the satellites' positions, $\bf{r}_{0}$ is the
positions pof the host DM halo, $\bf{1}$ is the unit matrix,  and
${\bf r}^T$ is the transposed vector $\bf{r}$. 
We finally compute the eigenvalues, $a>b>c$, and corresponding
eigenvectors, $\hat{I}_a$, $\hat{I}_b$, $\hat{I}_c$, of this tensor.
In the case of a sheet-like configuration the vector perpendicular to
the sheet would be signaled by, $\hat{I}_a$, the eigenvector of the
largest eigenvalue.

@@

We fit satellite planes around each galaxy in the pair by randomly
generating 10000 unit vectors over the  sphere, each vector
representing the direction perpendicular to a plane passing through
the main galaxy's center of mass. 
We compute the dot product of the unit vector with the position vector
for each satellite, this scalar gives us the satellite distance to the
plane. 
The best plane is determined by the vector that gives the lowest
position satellite distance dispersion. 
We take the dispersion value as a measure of the plane's width.
For comparison we store the value and direction giving the
highest distance dispersion.
We denote by $\hat{p}$ the unit vector defining the direction
perpendicular to the best plane.

@@

\begin{table*}
  \centering
\begin{tabular}{lll}
\hline\hline
Symbol & Units & Description\\\hline
$M_{\star}$ & $10^{10}$\Msun & Stellar mass\\
$N_s$ & & Number of satellites with $M_V<-9$\\
$a > b> c$ & & Inertia tensor eigenvalues. \\
$\hat{s}_1$, $\hat{s}_2$, $\hat{s}_3$ & & Inertia tensor eigenvectors. \\
$\beta$  &  & Satellite Velocity Anisotropy\\
$\sigma_s$ & kpc & Plane width\\
$\lambda_1>\lambda_2>\lambda_3$ &  & Hessian Matrix
eigenvalues\\
$\hat{e}_{1}$,  $\hat{e}_{2}$,  $\hat{e}_{3}$ & - & Hessian Matrix
eigenvectors\\ 
$\hat{r}_{AB}$& & Unit vector in the direction to the galaxy companion\\
\hline\hline
\end{tabular}
  \caption{Overview of the parameters computed for each central galaxy
    and its satellite system.
  \label{tab:models}}
\end{table*}

\subsection{Cosmic Web Alignment}
\label{sub:webalignment}

\cite{2015ApJ...799...45F} showed tha LGA pairs present alignments
with the cosmic web.
The strongest alignment is between the eigenvector associated  with the smallest
eigenvalue, $\hat{e}_3$, and the vector $\hat{r}_{AB} $connecting the two halos in
the pair. 
The eigenvector $\hat{e}_3$ indicates the direction along
which the cosmic web filament lies and in the case of being on a local
sheet it is a vector lying on the pancakes' plane.

Following \cite{} we want to find the cosmic web preferential
direction towards which the vectors $\hat{r}_{AB}$, $\hat{s}_3$ and

@@

%% Tambien deberiamos sacar las alineaciones con el momentum angular
%% de las estrellas de las galaxias principales.
